Exploring the Design Space of Differentially Private Bayesian Inference under Hellinger Distance

### 2019-01-23 ICML2019/main.tex
update section 7

@@

\begin{figure}
\begin{center}
\centering
    \includegraphics[width=0.35\textwidth]{privacyloss.eps}
\caption{Actual privacy loss of different data size when privacy bound $\epsilon = 1.0$ in 2 dimensions, prior:$\betad(1,1)$ and balanced data}
\label{fig_privacy}
\end{center}
\end{figure}

>>>>

The red box representing the $\expmech$ plays worst in terms of accuracy. While the orange one representing the $\hexpmech$ has a better performance even though they achieve the same privacy bound, because we are calibrating noise to the Hellinger distance (the accuracy metric we are using).

@@

\begin{figure}
\begin{center}
\centering
    \includegraphics[width=0.35\textwidth]{privacyloss.eps}
\caption{The privacy loss in practice under different data size when privacy bound $\epsilon = 1.0$ in 2 dimensions, prior:$\betad(1,1)$ and balanced data}
\label{fig_privacy}
\end{center}
\end{figure}
